Augraphy: A Data Augmentation Library for Document Images

### 2023-04-22 paper.tex
Remove anonymous header
Updated intro and motivation

\title{Augraphy: A Data Augmentation Library for Document Images}
%\author{Alexander Groleau\inst{1,2} \and
%Kok Wei Chee\inst{1} \and
%Samay Maini\inst{1} \and
%Jonathan Boarman\inst{1}}
%
%\authorrunning{A. Groleau et al.}
%
%\institute{Sparkfish LLC (\email{augraphy@sparkfish.com})
%\and
%Left Associates LLC (\email{research@left.associates})}

\author{Anonymous ICDAR 2023 submission}

@@

\section{Introduction and Motivation}
Daily life in the modern world is increasingly data-driven, involving myriad tasks which require the generation and handling of unstructured data.
Increasingly, this data occurs in the form of messages or images, often with complex contents.
In the office space, most data is created and stored document-form, easy to print and distribute.
The lifetime of these documents typically includes physical alterations by printing, scanning, or photocopying operations, so real documents may appear visually very different from their original born-digital counterparts.
Real-world processes can introduce many types of distortions: folds, wrinkles, or tears in a page can cause color changes and shadows in a scanned document image; low or high printer ink settings may cause some regions of a document to be lighter or darker; human-made annotations like highlighting or pencil marks can add noise to the page.

The outcomes of many machine learning operations involving documents are impacted by the presence of such noise; high-level tasks like document classification and information extraction are frequently expected to perform well even on noisily-scanned document images.
For instance, the RVL-CDIP document classification corpus \cite{harley2015icdar-rvlcdip} consists of scanned document images, many of which have substantial amounts of scanner-induced noise, as does the FUNSD form understanding benchmark \cite{jaume2019-funsd}.
Other intermediate-level tasks like optical character recognition (OCR) and page layout analysis may perform optimally if noise in a document image is minimized \cite{character-recognition-systems,ogorman-document-image-analysis,Rotman2022-hh}.
The lower-level task of document denoising tackles the document noise problem directly, by attempting to remove noise from a document image \cite{ref_noisyoffice,blind-denoising-iccv-2021,kulkarni-2020,patch-based-document-denoising,Mustafa_2018-wan}.
All of these tasks benefit from copious amounts of training data, and one way of generating large amounts of training data with noise-like artefacts is to use data augmentation, reducing the need for human toil.

@@

    \caption{\emph{Augraphy} can be used to introduce noisy perturbations to document images like the original noise seen above, which is a real-life sample from RVL-CDIP. We re-created a clean reproduction and then created a noisy version by applying several \emph{Augraphy} augmentations.}

@@

For this reason we introduce \emph{Augraphy}, an open-source Python-based data augmentation library for generating versions of document images that contain realistic noise artefacts commonly introduced via scanning, photocopying, and other office procedures.
\emph{Augraphy} differs from most image data augmentation tools by specifically targeting the types of alterations and degradations seen in document images.
\emph{Augraphy} offers \numAugraphyAugmentations ~individual augmentation methods out-of-the-box across three ``phases" of augmentations, and these individual phase augmentations can be composed together along with a ``paper factory" step where different paper backgrounds can be added to the augmented image.
The resulting images are realistic, noisy versions of clean documents, as evidenced in Figure~\ref{fig:intro}, where we apply several \emph{Augraphy} augmentations to a clean document image in order to mimic the types of noise seen in a real-world noisy document image from RVL-CDIP.

\emph{Augraphy} has been used in several research efforts: Larson et al. (2022) \cite{larson-2022-rvlcdip-ood} used \emph{Augraphy} to mimic scanner-like noise for evaluating document classifiers trained on RVL-CDIP; Jadhav et al 2022 \cite{jadhav2022pix2pix} used \emph{Augraphy} to generate noisy document images for training a document denoising GAN; and Kim et al. 2022 \cite{webvicob-2022-naver} used \emph{Augraphy} as part of a document generation pipeline for document understanding tasks.

This paper provides an overview of the \emph{Augraphy} library, and demonstrates how it can be used both as a training data augmentation tool and as an effective means for producing data for robustness testing.

>>>>

\title{Augraphy: A Data Augmentation Library for Document Images}
\author{Alexander Groleau\inst{1} \and
Kok Wei Chee\inst{1} \and
Stefan Larson\inst{2} \and
Samay Maini\inst{1} \and
Jonathan Boarman\inst{1}}

\authorrunning{A. Groleau et al.}

\institute{Sparkfish LLC (\email{augraphy@sparkfish.com}) \and
Vanderbilt University}

@@

\section{Introduction and Motivation}

The \emph{Augraphy} library is designed to produce training datasets, pairing synthetic dirty documents with their clean ground truth document image sources.  The need for such a data augmentation tool in document image analysis primarily results from the lack of ground truth images being available for most of the documents recorded within human history.  Access to the knowledge stored in such document images is thwarted by artifacts, distortion and noise.  As such, there is an ongoing need to improve available techniques to restore document images and thereby unlocking their contents for use in search or other document analysis tasks.

An ongoing digital transformation has reduced everyday reliance on paper.  However, major industries such as healthcare\cite{menachemi2011benefits}, insurance\cite{gatzert2016impact}, legal\cite{staudt2015access}, financial services\cite{chuen2017handbook}, government\cite{albano2018role}, and education\cite{alkhezzi2020factors} continue to produce physical documents that are later digitally archived.

Paper documents accumulate physical damage and alterations through printing, scanning, photocopying and daily life.  Real-world processes introduce many types of distortions that result in color changes, shadows in scanned documents, degraded text where low ink, annotations, highlighters or other markings add noise to the page that perturb semantic access by digital means.

@@

    \caption{\emph{Augraphy} can be used to introduce noisy perturbations to document images like the original noise seen above, which is a real-life sample from RVL-CDIP. We demonstrate this by creating a noisy reproduction via \emph{Augraphy} augmentations against a clean reproduction.}

@@

Document image analysis tasks are impacted by the presence of such noise; high-level tasks like document classification and information extraction are frequently expected to perform well even on noisily-scanned document images.
For instance, the RVL-CDIP document classification corpus \cite{harley2015icdar-rvlcdip} consists of scanned document images, many of which have substantial amounts of scanner-induced noise, as does the FUNSD form understanding benchmark \cite{jaume2019-funsd}.
Other intermediate-level tasks like optical character recognition (OCR) and page layout analysis may perform optimally if noise in a document image is minimized \cite{character-recognition-systems,ogorman-document-image-analysis,Rotman2022-hh}.

Attempts have been made to denoise document images in order to improve document tasks \cite{ref_noisyoffice,blind-denoising-iccv-2021,kulkarni-2020,patch-based-document-denoising,Mustafa_2018-wan}.  However, they have lacked the benefit of large datasets with ground truth images to train those denoisers.

A tool such as \emph{Augraphy} that helps to produce copious amounts of training data with document noise artefacts is essential in this space to developing advanced document binarization and denoising processes.

For this reason we introduce \emph{Augraphy}, an open-source Python-based data augmentation library for generating versions of document images that contain realistic noise artefacts commonly introduced via scanning, photocopying, and other office procedures.
\emph{Augraphy} differs from most image data augmentation tools by specifically targeting the types of alterations and degradations seen in document images.

\emph{Augraphy} offers \numAugraphyAugmentations ~individual augmentation methods out-of-the-box across three ``phases" of augmentations, and these individual phase augmentations can be composed together along with a ``paper factory" step where different paper backgrounds can be added to the augmented image.
The resulting images are realistic, noisy versions of clean documents, as evidenced in Figure~\ref{fig:intro}, where we apply \emph{Augraphy} augmentations to a clean document image in order to mimic the types of noise seen in a real-world noisy document image from RVL-CDIP.

Several research efforts have used \emph{Augraphy}: Larson et al. (2022) \cite{larson-2022-rvlcdip-ood} used \emph{Augraphy} to mimic scanner-like noise for evaluating document classifiers trained on RVL-CDIP; Jadhav et al 2022 \cite{jadhav2022pix2pix} used \emph{Augraphy} to generate noisy document images for training a document denoising GAN; and Kim et al. 2022 \cite{webvicob-2022-naver} used \emph{Augraphy} as part of a document generation pipeline for document understanding tasks.
